### 2020-07-15 paper/sections/design.tex
r1

\textcolor{revise}{As shown in Figure~\ref{fig: quality_chosen}, we find that in different cloud-based application environments, the agent's chosen compression quality levels can be quite different. We compute the \emph{mean} and \emph{standard deviation} of compression quality levels. The mean is respectively 33.4, 24.7 and 31.6 on Baidu Vison, Face++ and Amazon Rekognition. For Face++, the \emph{mean} of compression quality levels is lower than that for Baidu Vision. The standard deviation is respectively 22.77, 19.19 and 22.46 on Baidu Vison, Face++ and Amazon Rekognition.} The ``optimal'' compression strategies are different for different backend cloud services. This variation is caused by the interaction between the agent and the backend cloud model in the training phase. Since the agent's training procedure is based on a specific backend cloud model $ M_1 $, for another backend cloud model $ M_2 $, the interaction between the agent and $ M_2 $ is quite different. Therefore the agent's best compression quality level selection presents variation for different backend cloud models.

@@

Moreover, in our experiment, the agent presents different behaviors when the input image changes from one dataset to another. Figure~\ref{fig: dataset_change} shows the agent's choices for the same backend cloud model (Baidu Vision) but different image datasets. We prepare two datasets indicating two contextual ``sceneries''. We randomly sample images from ImageNet~\cite{ImageNet} whose images are mostly taken in the daytime, to act as a daytime scenery, and randomly select nighttime images from the FLIR Thermal Dataset~\cite{FLIR} to form another dataset to act as a nighttime scenery. \textcolor{revise}{The histogram shown in Figure~\ref{fig: dataset_change} points out that the distribution of compression quality levels is different on ImageNet and FLIR Thermal Dataset. For ImageNet and FLIR, the mean is respectively 43.3 and 47.5, and the standard deviation is respectively 19.52 and 26.56.} We can see that, to maintain high accuracy, when the input image's contextual group $ \mathcal{X} $ changes, the agent's compression quality level selection would change as well. This phenomenon presents that the agent can adaptively choose a proper compression quality level based on the input image's features.

\textcolor{revise}{We can also find that Figure~\ref{fig: quality_chosen}(a) and Figure~\ref{fig: dataset_change}(a) is different, even if we use the same cloud service (Baidu Vision) and image dataset (ImageNet). When we use the same cloud service at different times, the cloud service commonly invokes different backend cloud models. Therefore the interaction between the agent and the backend cloud model is different. This result variation presents that the agent can adaptively make a proper compression strategy in different complex environments, indicating our solution's generality and practicality.} %% \\

>>>>

\textcolor{revise}{As shown in Figure~\ref{fig: quality_chosen}, we find that in different cloud-based application environments, the agent's chosen compression quality levels can be quite different. We compute the \emph{mean} and \emph{standard deviation} of compression quality levels. The mean is $33.4$, $24.7$ and $31.6$ on Baidu Vison, Face++ and Amazon Rekognition, respectively. For Face++, the \emph{mean} of compression quality levels is lower than that for Baidu Vision. The standard deviation is $22.77$, $19.19$ and $22.46$ on Baidu Vison, Face++ and Amazon Rekognition, respectively.} The ``optimal'' compression strategies are different for different backend cloud services. This variation is caused by the interaction between the agent and the backend cloud model in the training phase. Since the agent's training procedure is based on a specific backend cloud model $ M_1 $, for another backend cloud model $ M_2 $, the interaction between the agent and $ M_2 $ is quite different. Therefore the agent's best compression quality level selection presents variation for different backend cloud models.

@@

Moreover, in our experiment, the agent presents different behaviors when the input image changes from one dataset to another. Figure~\ref{fig: dataset_change} shows the agent's choices for the same backend cloud model (Baidu Vision) but different image datasets. We prepare two datasets indicating two contextual ``sceneries''. We randomly sample images from ImageNet~\cite{ImageNet} whose images are mostly taken in the daytime, to act as a daytime scenery, and randomly select nighttime images from the FLIR Thermal Dataset~\cite{FLIR} to form another dataset to act as a nighttime scenery. \textcolor{revise}{The histogram shown in Figure~\ref{fig: dataset_change} points out that the distribution of compression quality levels is different on ImageNet and FLIR Thermal Dataset. For ImageNet and FLIR, the mean is 43.3 and 47.5, respectively; and the standard deviation is 19.52 and 26.56, respectively.} To maintain high accuracy when the input image's contextual group $ \mathcal{X} $ changes, the agent's compression quality level selection should change as well. This phenomenon presents that the agent can adaptively choose a proper compression quality level based on the input image's features.

\textcolor{revise}{We can also find that Figure~\ref{fig: quality_chosen}(a) and Figure~\ref{fig: dataset_change}(a) is different, even if we use the same cloud service (Baidu Vision) and image dataset (ImageNet). When we use the same cloud service at different times, the cloud service commonly invokes different backend cloud models. Therefore the interaction between the agent and the backend cloud model is different. This variation presents that the agent can adaptively make a proper compression strategy in different complex environments, indicating our solution's generality and practicality.} %% \\

### 2020-07-15 paper/sections/evaluation.tex
r1

\textcolor{revise}{In our experiments, the convergence condition of training is that the recent average accuracy over 0.8 meanwhile the recent average reward over 0.45. The experiment results show the number of training images is respectively 898 and 910 on ImageNet and FLIR. The time cost mainly depends on the frequency of sending images and the inference speed of the cloud service. If the end-user sends images continuously, and cloud service's inference speed is about 10 images per second, the time costs are respectively about 197.3s and 200.8s on ImageNet and FLIR. In the training phase, we need to upload reference images and compressed images. We consider the time cost of uploading reference images and obtaining the feedbacks as the benchmark latency. If we minus this benchmark latency, the real training time cost is not over 100s. It is worth to spend such upload size overhead and time cost at the beginning when we need to infer thousands of images.}

@@

\textcolor{revise}{The \emph{inference-estimation-querying-retraining} mechanism would either re-load or re-train a RL agent intelligently when capturing the scenery change. The re-training time cost is similar to the training time cost which is described above. The latency of re-loading a RL agent model is about 1.85s. To \emph{erase} this latency, we use another process to re-load the model in our experiments. The mechanism still uses the old RL agent to choose a compression quality level before the re-loading process has finished.}

>>>>

\textcolor{revise}{In our experiments, the convergence condition of training is that the recent average accuracy over 0.8 meanwhile the recent average reward over 0.45. The experiment results show the number of training images is 898 and 910 on ImageNet and FLIR, respectively. The time cost mainly depends on the frequency of sending images and the inference speed of the cloud service. If the end-user sends images continuously, and cloud service's inference speed is about 10 images per second, the time costs are 197.3s and 200.8s on ImageNet and FLIR, respectively. In the training phase, we need to upload reference images and compressed images. We consider the time cost of uploading reference images and obtaining the feedbacks as the benchmark latency. If we minus this benchmark latency, the real training time cost is not over 100s. It is worth to spend such upload size overhead and time cost at the beginning when we need to infer thousands of images.}

@@

\textcolor{revise}{The \emph{inference-estimation-querying-retraining} mechanism would either re-load or re-train a RL agent intelligently when capturing the scenery change. The re-training time cost is similar to the training time cost which is described above. The latency of re-loading a RL agent model is about 1.85s. To \emph{reduce} this latency, we use another process to re-load the model in our experiments. The mechanism still uses the old RL agent to choose a compression quality level before the re-loading process has finished.}
